---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CountMissingByGroup

<!-- badges: start -->

<!-- badges: end -->

Given a data frame `data` and a column `group`, `count_all_missing_by_group()` creates a new data frame with one row per level of `group`. The first column of the output data frame contains the levels of `group`, and the rest of the columns contain the number of missing values for all columns in `data` except `group`.

## Installation

You can install the development version of CountMissingByGroup from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/CountMissingByGroup", ref='0.1.0')
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(CountMissingByGroup)
count_all_missing_by_group(airquality, Month, .groups = "keep")
```
